Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_catalogue.tex
ontology references removed
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@867 d8b0c59b-6544-0410-94d9-83a5658a058e

The architecture comprises a RDF store used for persistence, a business layer dealing with the model and reasoning, and public façade providing the core functionality as a RESTful API, and a SPARQL endpoint accessing directly the RDF store. This presentation layer is aimed to interact with the FAST Gadget Visual Storyboard, or any other third-party application.

@@

The business logic layer contains all the domain-specific processing and reasoning. It provides functions to interact with all the elements of the domain model specified in \cite{ssec:ontology}, acting as a mediator between the public RESTful API and the persistence layer.

@@

\input{paper_ssec_ontology}

>>>>

The architecture comprises a RDF store used for persistence, a business layer dealing with the model and reasoning, and public facade providing the core functionality as a RESTful API, and a SPARQL endpoint accessing directly the RDF store. This presentation layer is aimed to interact with the FAST Gadget Visual Storyboard, or any other third-party application.

@@

The business logic layer contains all the domain-specific processing and reasoning. It provides functions to interact with all the elements of the domain model,
% specified in \ref{ssec:ontology}
acting as a mediator between the public RESTful API and the persistence layer.

@@

% \input{paper_ssec_ontology}

### 2010-06-14 trunk/papers/icsoc2010/paper_sec_use_case.tex
ontology references removed
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@867 d8b0c59b-6544-0410-94d9-83a5658a058e

Then, the web service wrapper tool, which is used to create the formal definitions of back-end services, transforming them into building blocks to be stored and reused within the FAST platform. It is integrated into the graphical IDE, and for the storage interacts with the catalogue, where the formal service descriptions and the executable code encapsulating the service behaviour is stored.

The publishing platform presented, called ``Resource Catalogue'' within the FAST platform, covers several important purposes:
\begin{description}
	\item[Publication and search of gadgets] The output of the FAST IDE are gadgets, which are self-contained and ready to use for users. They need to be made available for download, as well as being discover according to their formal description.
	\item[Publication and search of building blocks] Every single component or building block definition is stored in the catalogue and it provides powerful ways of searching, recommendation and planning. 
	\item[Storage and indexing of user profiles and histories] Each user of the FAST platform will have a representation in the catalogue, thus making it possible for the IDE to make informed guesses about what they want in a particular situation, based on their previous behaviour.
	\item[Facilitate ontology mediation] Because FAST allows the integration of third-party external services, it is not always guaranteed that all the data coming from a service is directly compatible with the FAST platform. In such cases, mediation between the different ontologies is necessary. The catalogue provide some grade of mediation functionality.
\end{description}

>>>>

The web service wrapper tool is then used to create the formal definitions of back-end services, transforming them into building blocks to be stored and reused within the FAST platform. The tool is integrated directly into the graphical IDE, and for the storage interacts with the catalogue, where the formal service descriptions and the executable code encapsulating the service behaviour is stored.

The publishing platform presented, called ``Metadata Catalogue'' within the FAST platform, covers several important purposes:
\begin{description}
	\item[Publication and search of gadgets] The output of the FAST IDE are gadgets, which are self-contained and ready to use for users. They need to be made available for download, as well as being discover according to their formal description.
	\item[Publication and search of building blocks] Every single component or building block definition is stored in the catalogue and it provides powerful ways of searching, recommendation and planning. 
	\item[Storage and indexing of user profiles and histories] Each user of the FAST platform will have a representation in the catalogue, thus making it possible for the IDE to make informed guesses about what they want in a particular situation, based on their previous behaviour.
	\item[Facilitate ontology mediation] Because FAST allows the integration of third-party external services, it is not always guaranteed that all the data coming from a service is directly compatible with the FAST platform. In such cases, mediation between the different ontologies is necessary. The catalogue provide some grade of mediation functionality.
\end{description}

### 2010-06-14 trunk/papers/icsoc2010/paper_ssec_ontology.tex
ontology references removed
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@867 d8b0c59b-6544-0410-94d9-83a5658a058e

\subsection{Simplified Model/Ontology (Knud)}
The model used to define the web service wrappers within this application has been influenced by WSDL, the main web service definition language, and some semantic-enriched approaches such as WSMO and OWL-S. There is no need to reinvent the wheel,

>>>>

%!TEX root = paper.tex

\subsection{Simplified Model/Ontology (Knud)}
\label{ssec:ontology}
The model used to define the web service wrappers within this application has been influenced by WSDL, the main web service definition language, and some semantic-enriched approaches such as WSMO and OWL-S. There is no need to reinvent the wheel,
